---
title: "Cherwell Weekly Aging Report"
date: "`r format(Sys.time(), '%d %B, %Y')`" 
output: "html_document"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, out.width='90%')
pagebreak <- function() {
  if(knitr::is_latex_output())
    return("\\newpage")
  else
    return('<div style="page-break-before: always;" />')
}
```


```{r File open and setup, include=FALSE}
#
# Library setups
#

# Import libraries
library(tidyverse)
library(tidyr)
library(plyr)
library(dplyr)
library(caret)
library(ggplot2)
library(ggthemes)
library(extrafont)
library(scales)
library(reshape2)
library(stringi)
library(expss)
library(grid)
library(gridExtra)
library(lattice)
library(janitor)
library(rmarkdown)
library(kableExtra)
library(lubridate)
library(scales)

#--------------------------------------------------------------------
#
# File open, cleanup, and set up for the analysis
#
#--------------------------------------------------------------------

#
# Download and open survey file
#


# Import and Open the data file / Establish the data set
data_filename <- "0_Input_Open_Tickets_190829.csv"
dat <- read.csv(file = data_filename, skip = 1, header = TRUE, stringsAsFactors = FALSE) 

# Clean up column / vector names
dat <- rename(dat, replace = c("Incident.ID" = "ID",
                               "Created.Date.Time" = "Created",
                               "Customer.Display.Name" = "Customer",
                               "Incident.Type" = "Type",
                               "Short.Description" = "Desc",
                               "Owned.By" = "Owner",
                               "SLA.Resolve.By.Deadline" = "Due"))

# Get rid of unneeded column and row information and sort by created date
dat <- dat %>% select(ID, Created, Customer, Type, Desc, Owner, Due)
dat <- dat %>% filter(dat$Created != "")

# Shorten some fields
dat[dat == "Incident"]            <- "Inc"
dat[dat == "Service Request"]     <- "SR"

# Simplify timestamp to simple dates
dat$Created <- sub(' .*', '', dat$Created)
dat$Created <- as.Date(dat$Created, format = "%m/%d/%Y")

dat$Due <- sub(' .*', '', dat$Due)
dat$Due <- as.Date(dat$Due, format = "%m/%d/%Y")

# Add column for days open (Duration)
dat <- dat %>% mutate(Duration = difftime(Sys.Date(), dat$Created, units = "days"))
dat <- dat %>% arrange(desc(Duration))

# Establish groupings for the open tickets
days_07 <- dat %>% filter(Duration <=  7) %>% select(-Desc)
days_30 <- dat %>% filter(Duration <= 30 & Duration >  7) %>% select(-Desc)
days_60 <- dat %>% filter(Duration <= 60 & Duration > 30) %>% select(-Desc)
over_60 <- dat %>% filter(Duration >  60) %>% select(-Desc)

# Establish groupings for SLA compliance
inc_sla      <- dat %>% filter(Type == "Inc" & Duration <=  2) %>% select(-Desc)
inc_sla_perc <- (nrow(inc_sla) / nrow(dat %>% filter(Type == "Inc"))) * 100
inc_sla_perc <- round(inc_sla_perc, digits = 2)

SR_sla       <- dat %>% filter(Type =="SR" & Duration <= 10) %>% select(-Desc)
SR_sla_perc  <- (nrow(SR_sla) / nrow(dat %>% filter(Type == "SR"))) * 100
SR_sla_perc  <- round(SR_sla_perc, digits = 2)

```

===========================================================================

**Part  1 - Tickets Sorted by Owner Within Age**

===========================================================================

**Total open tickets: `r nrow(dat)` / Incidents: `r nrow(dat %>% filter(Type == "Inc"))` / SR's: `r nrow(dat %>% filter(Type == "SR"))`**  
Incidents meeting SLA guidelines: `r inc_sla_perc` %  
Service Requests meeting SLA guidelines: `r SR_sla_perc` %

===========================================================================  
Group 1: Aged over 60 Days - `r nrow(over_60)` tickets `r round((nrow(over_60) / nrow(dat) * 100), digits = 2)` % of total  
===========================================================================  

```{r 1-1 60 Day Summary, echo=FALSE, comment=NA}

over_60 <- over_60 %>% arrange(Owner, desc(Duration))
knitr::kable(over_60) %>%
  kable_styling(bootstrap_options = "striped", full_width = F, position = "left")
cat("\n")
```

===========================================================================  
Group 2: Aged 30 - 60 Days - `r nrow(days_60)` tickets `r round((nrow(days_60) / nrow(dat) * 100), digits = 2)` % of total  
===========================================================================  

```{r 1-2 30 to 60 Summary, echo=FALSE}

days_60 <- days_60 %>% arrange(Owner, desc(Duration))
knitr::kable(days_60) %>%
  kable_styling(bootstrap_options = "striped", full_width = F, position = "left")
cat("\n")
```

===========================================================================  
Group 3: Aged up to 30 Days - `r nrow(days_30)` tickets `r round((nrow(days_30) / nrow(dat) * 100), digits = 2)` % of total  
===========================================================================  

```{r 1-3 Up to 30 Days Summary, echo=FALSE}
days_30 <- days_30 %>% arrange(Owner, desc(Duration))
knitr::kable(days_30) %>%
  kable_styling(bootstrap_options = "striped", full_width = F, position = "left")
cat("\n")
```

===========================================================================  
Group 4: Aged 1 Week or Less - `r nrow(days_07)` tickets `r round((nrow(days_07) / nrow(dat) * 100), digits = 2)` % of total  
===========================================================================  

```{r 1-4 Summary up to 7 days, echo=FALSE}
days_07 <- days_07 %>% arrange(Owner, desc(Duration))
knitr::kable(days_07) %>%
  kable_styling(bootstrap_options = "striped", full_width = F, position = "left")
cat("\n")
```

`r pagebreak()`

=============2=============================================================  
Part 2: Graphics  
===========================================================================  

```{r Graphics Section, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
#--------------------------------------------------------------------
#
# Build graphics from historical data
#
#--------------------------------------------------------------------

# Open File
data_filename <- "0_Output_cherwell_stats.csv"
dat <- read.csv(file = data_filename, header = TRUE, stringsAsFactors = FALSE)

# Force the dates to sort (and plot) in ascending order
dat$Week_Ending <- as.character(dat$Week_Ending)
dat$Week_Ending <- factor(dat$Week_Ending, levels=unique(dat$Week_Ending))

# Number of Opens by Week
Opens_by_Week <- ggplot() +
     geom_line(data = dat, aes(x = dat$Week_Ending, y = dat$Opens, color = "Opens", group = 1), size = 1.5) +
     theme_economist() +
     scale_y_continuous(limits=c(0, 500)) +
     theme(axis.text.x=element_text(angle=90,hjust=1,vjust=0.5)) +
     theme(legend.title = element_blank()) +
     labs(title = "Number of Opens", subtitle = "By Week") + xlab("Week") + ylab("Number")

# Display plot
Opens_by_Week
```

`r pagebreak()`

```{r Overall stats graph, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
# Number of incidents meeting SLAs
inc_mtg_slas <- ggplot() +
     geom_line(data = dat, aes(x = dat$Week_Ending, y = dat$Inc_Mtg_SLA, color = "SLA %", group = 1), size = 1.5) +
     theme_economist() +
     scale_y_continuous(limits=c(0, 20)) +
     theme(axis.text.x=element_text(angle=90,hjust=1,vjust=0.5)) +
     theme(legend.title = element_blank()) +
     labs(title = "% Incidents Meeting SLA", subtitle = "By Week") + xlab("Week") + ylab("Number")

# Number of service requests meeting SLAs
sr_mtg_slas <- ggplot() +
     geom_line(data = dat, aes(x = dat$Week_Ending, y = dat$SR_Mtg_SLA, color = "SLA %", group = 1), size = 1.5) +
     theme_economist() +
     scale_y_continuous(limits=c(0, 20)) +
     theme(axis.text.x=element_text(angle=90,hjust=1,vjust=0.5)) +
     theme(legend.title = element_blank()) +
     labs(title = "% SRs Meeting SLA", subtitle = "By Week") + xlab("Week") + ylab("Number")

# Arrange the plots
grid.arrange(inc_mtg_slas, sr_mtg_slas, ncol = 2)
```

`r pagebreak()`

```{r Days outputs, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
# Number of 7 days
plot_days07 <- ggplot() +
     geom_line(data = dat, aes(x = dat$Week_Ending, y = dat$Days_07, color = "Days <= 7", group = 1), size = 1.5) +
     scale_y_continuous(limits=c(0, 150)) +
     theme_economist() +
     theme(axis.text.x=element_text(angle=90,hjust=1,vjust=0.5)) +
     theme(legend.title = element_blank()) +
     labs(title = "Tickets Open 7 Days or Less", subtitle = "By Week") + xlab("Week") + ylab("Number")

# Number of 30 days
plot_days30 <- ggplot() +
     geom_line(data = dat, aes(x = dat$Week_Ending, y = dat$Days_30, color = "Days <= 30", group = 1), size = 1.5) +
     scale_y_continuous(limits=c(0, 150)) +
     theme_economist() +
     theme(axis.text.x=element_text(angle=90,hjust=1,vjust=0.5)) +
     theme(legend.title = element_blank()) +
     labs(title = "Tickets Open 8 to 30 Days", subtitle = "By Week") + xlab("Week") + ylab("Number")

# Arrange the plots
grid.arrange(plot_days07, plot_days30, ncol = 2)
```

```{r Remaining days plots, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
# Number up to 60 days
plot_days60 <- ggplot() +
     geom_line(data = dat, aes(x = dat$Week_Ending, y = dat$Days_60, color = "Days <= 60", group = 1), size = 1.5) +
     scale_y_continuous(limits=c(0, 150)) +
     theme_economist() +
     theme(axis.text.x=element_text(angle=90,hjust=1,vjust=0.5)) +
     theme(legend.title = element_blank()) +
     labs(title = "Tickets Open 31 to 60 Days", subtitle = "By Week") + xlab("Week") + ylab("Number")

# Number over 60
plot_over60 <- ggplot() +
     geom_line(data = dat, aes(x = dat$Week_Ending, y = dat$Over_60, color = "Days over 60", group = 1), size = 1.5) +
     scale_y_continuous(limits=c(0, 150)) +
     theme_economist() +
     theme(axis.text.x=element_text(angle=90,hjust=1,vjust=0.5)) +
     theme(legend.title = element_blank()) +
     labs(title = "Tickets Open Over 60 Days", subtitle = "By Week") + xlab("Week") + ylab("Number")

# Arrange the plots
grid.arrange(plot_days60, plot_over60, ncol = 2)
```

**End of Report**
