---
title: "Cherwell Weekly Aging Report"
date: "`r format(Sys.time(), '%d %B, %Y')`" 
output: "html_document"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, out.width='90%')
pagebreak <- function() {
  if(knitr::is_latex_output())
    return("\\newpage")
  else
    return('<div style="page-break-before: always;" />')
}
```


```{r File open and setup, include=FALSE}
#
# Library setups
#

library(tidyverse)
library(tidyr)
library(plyr)
library(dplyr)
library(caret)
library(ggplot2)
library(ggthemes)
library(extrafont)
library(scales)
library(stringi)
library(grid)
library(gridExtra)
library(lattice)
library(janitor)
library(rmarkdown)
library(kableExtra)
library(lubridate)
library(stringr)
library(googlesheets)

#--------------------------------------------------------------------
#
# File open, cleanup, and set up for the analysis
#
#--------------------------------------------------------------------

#
# Open the Google Sheet
#

# Open the data file - a Google Sheet in user's top level directory
data_filename <- gs_title("CAR-input-2019-10-25")
dat <- gs_read(data_filename, skip = 1, header = TRUE, stringsAsFactors = FALSE)

# Generate the week ending data from the data file name
Week_Ending <- str_sub(data_filename[2], 11, 20)

# Clean up column / vector names
dat <- rename(dat, replace = c("Incident ID" = "ID",
                               "Created Date Time" = "Created",
                               "Customer Display Name" = "Customer",
                               "Incident Type" = "Type",
                               "Owned By" = "Owner",
                               "SLA Resolve By Deadline" = "Due"))

# Get rid of unneeded column and row information and sort by created date
dat <- dat %>% select(ID, Created, Customer, Type, Owner, Due)
dat <- dat %>% filter(dat$Created != "")

# Shorten some fields
dat[dat == "Incident"]            <- "Inc"
dat[dat == "Service Request"]     <- "SR"

# Simplify timestamp to simple dates
dat$Created <- sub(' .*', '', dat$Created)
dat$Created <- as.Date(dat$Created, format = "%m/%d/%Y")

dat$Due <- sub(' .*', '', dat$Due)
dat$Due <- as.Date(dat$Due, format = "%m/%d/%Y")

# Add column for days open (Duration)
dat <- dat %>% mutate(Duration = difftime(as.Date(Week_Ending), dat$Created, units = "days"))
dat <- dat %>% arrange(desc(Duration))

# Establish groupings for the open tickets
days_07 <- dat %>% filter(Duration <=  7) 
days_30 <- dat %>% filter(Duration <= 30 & Duration >  7) 
days_60 <- dat %>% filter(Duration <= 60 & Duration > 30) 
over_60 <- dat %>% filter(Duration >  60) 

# Establish groupings for SLA compliance
inc_sla      <- dat %>% filter(Type == "Inc" & Duration <=  2) 
inc_sla_perc <- (nrow(inc_sla) / nrow(dat %>% filter(Type == "Inc"))) * 100
inc_sla_perc <- round(inc_sla_perc, digits = 2)

SR_sla       <- dat %>% filter(Type =="SR" & Duration <= 10) 
SR_sla_perc  <- (nrow(SR_sla) / nrow(dat %>% filter(Type == "SR"))) * 100
SR_sla_perc  <- round(SR_sla_perc, digits = 2)

#
# Capture statistics for this week and append to file
#

Opens         <- nrow(dat)
Incidents     <- nrow(dat %>% filter(Type == "Inc"))
Inc_Percent   <- round(((Incidents / Opens) * 100), digits = 1)
Inc_Mtg_SLA   <- inc_sla_perc
SRs           <- nrow(dat %>% filter(Type == "SR"))
SR_Percent    <- round(((SRs / Opens) * 100), digits = 1)
SR_Mtg_SLA    <- SR_sla_perc
Days_07       <- nrow(days_07)
Days_30       <- nrow(days_30)
Days_60       <- nrow(days_60)
Over_60       <- nrow(over_60)

# Create dataframe to hold the results for writing to the file
week_ending_data <- data.frame(Week_Ending,
                               Opens,
                               Incidents,
                               Inc_Percent,
                               Inc_Mtg_SLA,
                               SRs,
                               SR_Percent,
                               SR_Mtg_SLA,
                               Days_07,
                               Days_30,
                               Days_60,
                               Over_60)

# Open historical data file and append current week's data
output_file <- gs_title("CAR-output-cherwell-stats")
gs_add_row(output_file, ws = 1, input = week_ending_data, verbose = FALSE)

# Part 1 - ticket sorted by age within owner

owner_durs <- dat %>% arrange(Owner, desc(Duration)) 

# Open file with list of staff names
staff_filename <- gs_title("CAR-SD_Staff_List")
staff_list     <- gs_read(staff_filename, header = TRUE, stringsAsFactors = TRUE)
sd_staff       <- staff_list %>% filter(WAR == "Y") %>% select(Owner)
nsd_staff      <- staff_list %>% filter(WAR == "N") %>% select(Owner)

no_sd_staff    <- length(sd_staff$Owner)

# Create a list to hold Service Desk Staff groupings
sd_data_list   <- list()

#Loop to generate groupings and populate the list
for (i in 1:no_sd_staff) {
     x <- owner_durs %>% filter(Owner == sd_staff$Owner[i])
     sd_data_list[[i]] = data.frame(x)
}

```


**Total open tickets: `r nrow(dat)` / Incidents: `r nrow(dat %>% filter(Type == "Inc"))` / SR's: `r nrow(dat %>% filter(Type == "SR"))`**  
Incidents meeting SLA guidelines: `r inc_sla_perc` %  
Service Requests meeting SLA guidelines: `r SR_sla_perc` %

===========================================================================

**Part 1 - Service Desk Team - Tickets by Owner Sorted by Age**

===========================================================================

`r pagebreak()`

```{r sln1, echo=FALSE, comment=NA}

i <- 1

cat(">>>", sd_staff$Owner[i], "Total tickets:", nrow(sd_data_list[[i]]), "\n")

if(nrow(sd_data_list[[i]]) == 0) {
     cat("No current tickets for", sd_staff$Owner[i])
} else {
     knitr::kable(sd_data_list[[i]]) %>%
  kable_styling(bootstrap_options = "striped", full_width = F, position = "left")
}
```

`r pagebreak()`

```{r sln2, echo=FALSE, comment=NA}

if(no_sd_staff != i) {
     i <- i + 1
} else {
     cat("All staff have been processed", "\n")
}

cat(">>>", sd_staff$Owner[i], "Total tickets:", nrow(sd_data_list[[i]]), "\n")

if(nrow(sd_data_list[[i]]) == 0) {
     cat("No current tickets for", sd_staff$Owner[i])
} else {
     knitr::kable(sd_data_list[[i]]) %>%
  kable_styling(bootstrap_options = "striped", full_width = F, position = "left")
}
```

`r pagebreak()`

```{r sln3, echo=FALSE, comment=NA}

if(no_sd_staff != i) {
     i <- i + 1
} else {
     cat("All staff have been processed", "\n")
}

cat(">>>", sd_staff$Owner[i], "Total tickets:", nrow(sd_data_list[[i]]), "\n")

if(nrow(sd_data_list[[i]]) == 0) {
     cat("No current tickets for", sd_staff$Owner[i])
} else {
     knitr::kable(sd_data_list[[i]]) %>%
  kable_styling(bootstrap_options = "striped", full_width = F, position = "left")
}
```

`r pagebreak()`

```{r sln4, echo=FALSE, comment=NA}

if(no_sd_staff != i) {
     i <- i + 1
} else {
     cat("All staff have been processed", "\n")
}

cat(">>>", sd_staff$Owner[i], "Total tickets:", nrow(sd_data_list[[i]]), "\n")

if(nrow(sd_data_list[[i]]) == 0) {
     cat("No current tickets for", sd_staff$Owner[i])
} else {
     knitr::kable(sd_data_list[[i]]) %>%
  kable_styling(bootstrap_options = "striped", full_width = F, position = "left")
}
```

`r pagebreak()`

```{r sln5, echo=FALSE, comment=NA}

if(no_sd_staff != i) {
     i <- i + 1
} else {
     cat("All staff have been processed", "\n")
}

cat(">>>", sd_staff$Owner[i], "Total tickets:", nrow(sd_data_list[[i]]), "\n")

if(nrow(sd_data_list[[i]]) == 0) {
     cat("No current tickets for", sd_staff$Owner[i])
} else {
     knitr::kable(sd_data_list[[i]]) %>%
  kable_styling(bootstrap_options = "striped", full_width = F, position = "left")
}
```

`r pagebreak()`

```{r sln6, echo=FALSE, comment=NA}

if(no_sd_staff != i) {
     i <- i + 1
} else {
     cat("All staff have been processed", "\n")
}

cat(">>>", sd_staff$Owner[i], "Total tickets:", nrow(sd_data_list[[i]]), "\n")

if(nrow(sd_data_list[[i]]) == 0) {
     cat("No current tickets for", sd_staff$Owner[i])
} else {
     knitr::kable(sd_data_list[[i]]) %>%
  kable_styling(bootstrap_options = "striped", full_width = F, position = "left")
}
```

`r pagebreak()`

```{r sln7, echo=FALSE, comment=NA}

if(no_sd_staff != i) {
     i <- i + 1
} else {
     cat("All staff have been processed", "\n")
}

cat(">>>", sd_staff$Owner[i], "Total tickets:", nrow(sd_data_list[[i]]), "\n")

if(nrow(sd_data_list[[i]]) == 0) {
     cat("No current tickets for", sd_staff$Owner[i])
} else {
     knitr::kable(sd_data_list[[i]]) %>%
  kable_styling(bootstrap_options = "striped", full_width = F, position = "left")
}

if(no_sd_staff != i) {
     i <- i + 1
} else {
     cat("All staff have been processed", "\n")
}
```

`r pagebreak()`

===========================================================================

**Part  2 - Remaining Tickets Sorted by Non-Service Desk Owner**  


```{r 1-1 60 Day Summary, echo=FALSE, comment=NA}

# Set up the piles of SD staff tickets, Other owner tickets, unassigned tickets
nsd_dat <- merge(x = dat, y = nsd_staff, by = "Owner") 
una_dat <- dat %>% filter(Owner == unique(dat$Owner[6])) 
nsd_dat <- rbind(nsd_dat, una_dat) %>% arrange(Owner, desc(Duration))

# Establish groupings for the open tickets - but without sd staff included
nsd_days_07 <- nsd_dat %>% filter(Duration <=  7) 
nsd_days_30 <- nsd_dat %>% filter(Duration <= 30 & Duration >  7) 
nsd_days_60 <- nsd_dat %>% filter(Duration <= 60 & Duration > 30) 
nsd_over_60 <- nsd_dat %>% filter(Duration >  60) 
```

===========================================================================  
**Group 1: Total Tickets over 60 Days: `r nrow(over_60)` (`r round((nrow(over_60) / nrow(dat) * 100), digits = 2)` % of total)**  
**Non-Service Desk Tickets: `r nrow(nsd_over_60)`**  
===========================================================================  

```{r NSD1 60 Day Summary, echo=FALSE, comment=NA}

nsd_over_60 <- nsd_over_60 %>% arrange(Owner, desc(Duration))
knitr::kable(nsd_over_60) %>%
  kable_styling(bootstrap_options = "striped", full_width = F, position = "left")
cat("\n")
```

===========================================================================  
**Group 2: Total Tickets Aged 30 - 60 Days: `r nrow(days_60)` (`r round((nrow(days_60) / nrow(dat) * 100), digits = 2)` % of total)**  
**Non-Service Desk Tickets: `r nrow(nsd_days_60)`**  
===========================================================================  

```{r 1-2 30 to 60 Summary, echo=FALSE}

nsd_days_60 <- nsd_days_60 %>% arrange(Owner, desc(Duration))
knitr::kable(nsd_days_60) %>%
  kable_styling(bootstrap_options = "striped", full_width = F, position = "left")
cat("\n")
```

===========================================================================  
**Group 3: Total Tickets Aged up to 30 Days: `r nrow(days_30)` (`r round((nrow(days_30) / nrow(dat) * 100), digits = 2)` % of total)**  
**Non-Service Desk Tickets: `r nrow(nsd_days_30)`**  
===========================================================================  

```{r 1-3 Up to 30 Days Summary, echo=FALSE}
nsd_days_30 <- nsd_days_30 %>% arrange(Owner, desc(Duration))
knitr::kable(nsd_days_30) %>%
  kable_styling(bootstrap_options = "striped", full_width = F, position = "left")
cat("\n")
```

===========================================================================  
**Group 4: Total Tickets Aged 1 Week or Less: `r nrow(days_07)` (`r round((nrow(days_07) / nrow(dat) * 100), digits = 2)` % of total)**  
**Non-Service Desk Tickets: `r nrow(nsd_days_07)`**  
===========================================================================  

```{r 1-4 Summary up to 7 days, echo=FALSE}
nsd_days_07 <- nsd_days_07 %>% arrange(Owner, desc(Duration))
knitr::kable(nsd_days_07) %>%
  kable_styling(bootstrap_options = "striped", full_width = F, position = "left")
cat("\n")
```

`r pagebreak()`

===========================================================================  
Part 3 - Graphics  
===========================================================================  

```{r Graphics Section, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}

#--------------------------------------------------------------------
#
# Build graphics from historical data
#
#--------------------------------------------------------------------

# Open File
data_filename <- gs_title("CAR-output-cherwell-stats")
dat <- gs_read(data_filename, header = TRUE, stringsAsFactors = FALSE)

# Limit the number of weeks displayed to the most recent 3 months / quarter
dat <- tail(dat, 13)

# Force the dates to sort (and plot) in ascending order
dat$Week_Ending <- as.character(dat$Week_Ending)
dat$Week_Ending <- factor(dat$Week_Ending, levels=unique(dat$Week_Ending))

# Number of Opens by Week
Opens_by_Week <- ggplot() +
     geom_line(data = dat, aes(x = dat$Week_Ending, y = dat$Opens, color = "Opens", group = 1), size = 1.5) +
     theme_economist() +
     scale_y_continuous(limits=c(0, 500)) +
     theme(axis.text.x=element_text(angle=90,hjust=1,vjust=0.5)) +
     theme(legend.title = element_blank()) +
     labs(title = "Number of Opens", subtitle = "By Week") + xlab("Week") + ylab("Number")

# Display plot
Opens_by_Week
```

`r pagebreak()`

```{r Overall stats graph, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
# Number of incidents meeting SLAs
inc_mtg_slas <- ggplot() +
     geom_line(data = dat, aes(x = dat$Week_Ending, y = dat$Inc_Mtg_SLA, color = "SLA %", group = 1), size = 1.5) +
     theme_economist() +
     scale_y_continuous(limits=c(0, 50)) +
     theme(axis.text.x=element_text(angle=90,hjust=1,vjust=0.5)) +
     theme(legend.title = element_blank()) +
     labs(title = "% Incidents Meeting SLA", subtitle = "By Week") + xlab("Week") + ylab("Number")

# Number of service requests meeting SLAs
sr_mtg_slas <- ggplot() +
     geom_line(data = dat, aes(x = dat$Week_Ending, y = dat$SR_Mtg_SLA, color = "SLA %", group = 1), size = 1.5) +
     theme_economist() +
     scale_y_continuous(limits=c(0, 50)) +
     theme(axis.text.x=element_text(angle=90,hjust=1,vjust=0.5)) +
     theme(legend.title = element_blank()) +
     labs(title = "% SRs Meeting SLA", subtitle = "By Week") + xlab("Week") + ylab("Number")

# Arrange the plots
grid.arrange(inc_mtg_slas, sr_mtg_slas, ncol = 2)
```

`r pagebreak()`

```{r Days outputs, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
# Number of 7 days
plot_days07 <- ggplot() +
     geom_line(data = dat, aes(x = dat$Week_Ending, y = dat$Days_07, color = "Days <= 7", group = 1), size = 1.5) +
     scale_y_continuous(limits=c(0, 150)) +
     theme_economist() +
     theme(axis.text.x=element_text(angle=90,hjust=1,vjust=0.5)) +
     theme(legend.title = element_blank()) +
     labs(title = "Tickets Open 7 Days or Less", subtitle = "By Week") + xlab("Week") + ylab("Number")

# Number of 30 days
plot_days30 <- ggplot() +
     geom_line(data = dat, aes(x = dat$Week_Ending, y = dat$Days_30, color = "Days <= 30", group = 1), size = 1.5) +
     scale_y_continuous(limits=c(0, 150)) +
     theme_economist() +
     theme(axis.text.x=element_text(angle=90,hjust=1,vjust=0.5)) +
     theme(legend.title = element_blank()) +
     labs(title = "Tickets Open 8 to 30 Days", subtitle = "By Week") + xlab("Week") + ylab("Number")

# Arrange the plots
grid.arrange(plot_days07, plot_days30, ncol = 2)
```

```{r Remaining days plots, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
# Number up to 60 days
plot_days60 <- ggplot() +
     geom_line(data = dat, aes(x = dat$Week_Ending, y = dat$Days_60, color = "Days <= 60", group = 1), size = 1.5) +
     scale_y_continuous(limits=c(0, 150)) +
     theme_economist() +
     theme(axis.text.x=element_text(angle=90,hjust=1,vjust=0.5)) +
     theme(legend.title = element_blank()) +
     labs(title = "Tickets Open 31 to 60 Days", subtitle = "By Week") + xlab("Week") + ylab("Number")

# Number over 60
plot_over60 <- ggplot() +
     geom_line(data = dat, aes(x = dat$Week_Ending, y = dat$Over_60, color = "Days over 60", group = 1), size = 1.5) +
     scale_y_continuous(limits=c(0, 150)) +
     theme_economist() +
     theme(axis.text.x=element_text(angle=90,hjust=1,vjust=0.5)) +
     theme(legend.title = element_blank()) +
     labs(title = "Tickets Open Over 60 Days", subtitle = "By Week") + xlab("Week") + ylab("Number")

# Arrange the plots
grid.arrange(plot_days60, plot_over60, ncol = 2)
```

**End of Report**
