---
title: "Cherwell Weekly Aging Report"
date: "October 31, 2019"
output: pdf_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r File open and setup, include=FALSE}
#
# Library setups
#

library(tidyverse)
library(tidyr)
library(plyr)
library(dplyr)
library(knitr)
library(rmarkdown)
library(stringr)
library(googlesheets)

#--------------------------------------------------------------------
#
# File open, cleanup, and set up for the analysis
#
#--------------------------------------------------------------------

#
# Open the Google Sheet
#

# Open the data file - a Google Sheet in user's top level directory
data_filename <- gs_title("CAR-input-2019-10-25")
dat <- gs_read(data_filename, skip = 1, header = TRUE, stringsAsFactors = FALSE)

# Generate the week ending data from the data file name
Week_Ending <- str_sub(data_filename[2], 11, 20)

# Clean up column / vector names
dat <- rename(dat, replace = c("Incident ID" = "ID",
                               "Created Date Time" = "Created",
                               "Customer Display Name" = "Customer",
                               "Incident Type" = "Type",
                               "Owned By" = "Owner",
                               "SLA Resolve By Deadline" = "Due"))

# Get rid of unneeded column and row information and sort by created date
dat <- dat %>% select(ID, Created, Customer, Type, Owner, Due)
dat <- dat %>% filter(dat$Created != "")

# Shorten some fields
dat[dat == "Incident"]            <- "Inc"
dat[dat == "Service Request"]     <- "SR"

# Simplify timestamp to simple dates
dat$Created <- sub(' .*', '', dat$Created)
dat$Created <- as.Date(dat$Created, format = "%m/%d/%Y")

dat$Due <- sub(' .*', '', dat$Due)
dat$Due <- as.Date(dat$Due, format = "%m/%d/%Y")

# Add column for days open (Duration)
dat <- dat %>% mutate(Duration = difftime(as.Date(Week_Ending), dat$Created, units = "days"))
dat <- dat %>% arrange(desc(Duration))

# Establish groupings for the open tickets
days_07 <- dat %>% filter(Duration <=  7) 
days_30 <- dat %>% filter(Duration <= 30 & Duration >  7) 
days_60 <- dat %>% filter(Duration <= 60 & Duration > 30) 
over_60 <- dat %>% filter(Duration >  60) 

# Establish groupings for SLA compliance
inc_sla      <- dat %>% filter(Type == "Inc" & Duration <=  2) 
inc_sla_perc <- (nrow(inc_sla) / nrow(dat %>% filter(Type == "Inc"))) * 100
inc_sla_perc <- round(inc_sla_perc, digits = 2)

SR_sla       <- dat %>% filter(Type =="SR" & Duration <= 10) 
SR_sla_perc  <- (nrow(SR_sla) / nrow(dat %>% filter(Type == "SR"))) * 100
SR_sla_perc  <- round(SR_sla_perc, digits = 2)

#
# Capture statistics for this week and append to file
#

Opens         <- nrow(dat)
Incidents     <- nrow(dat %>% filter(Type == "Inc"))
Inc_Percent   <- round(((Incidents / Opens) * 100), digits = 1)
Inc_Mtg_SLA   <- inc_sla_perc
SRs           <- nrow(dat %>% filter(Type == "SR"))
SR_Percent    <- round(((SRs / Opens) * 100), digits = 1)
SR_Mtg_SLA    <- SR_sla_perc
Days_07       <- nrow(days_07)
Days_30       <- nrow(days_30)
Days_60       <- nrow(days_60)
Over_60       <- nrow(over_60)

# Create dataframe to hold the results for writing to the file
week_ending_data <- data.frame(Week_Ending,
                               Opens,
                               Incidents,
                               Inc_Percent,
                               Inc_Mtg_SLA,
                               SRs,
                               SR_Percent,
                               SR_Mtg_SLA,
                               Days_07,
                               Days_30,
                               Days_60,
                               Over_60)

# Open historical data file and append current week's data
# output_file <- gs_title("CAR-output-cherwell-stats")
# gs_add_row(output_file, ws = 1, input = week_ending_data, verbose = FALSE)

# Part 1 - ticket sorted by age within owner

owner_durs <- dat %>% arrange(Owner, desc(Duration)) 

# Open file with list of staff names
staff_filename <- gs_title("CAR-SD_Staff_List")
staff_list     <- gs_read(staff_filename, header = TRUE, stringsAsFactors = TRUE)
sd_staff       <- staff_list %>% filter(WAR == "Y") %>% select(Owner)
nsd_staff      <- staff_list %>% filter(WAR == "N") %>% select(Owner)

no_sd_staff    <- length(sd_staff$Owner)


```


**Total open tickets: `r nrow(dat)` / Incidents: `r nrow(dat %>% filter(Type == "Inc"))` / SR's: `r nrow(dat %>% filter(Type == "SR"))`**  
Incidents meeting SLA guidelines: `r inc_sla_perc` %  
Service Requests meeting SLA guidelines: `r SR_sla_perc` %

===========================================================================

**Part 1 - Service Desk Team - Tickets by Owner Sorted by Age**

===========================================================================

```{r Print out staff data, warning=FALSE, , echo=FALSE, results="asis"}

cat("\n\\newpage\n")

for(i in 1:no_sd_staff) {
     x <- owner_durs %>% filter(Owner == sd_staff$Owner[i])
     cat(sd_staff$Owner[i], "\n")
     if(nrow(x) == 0) {
          cat("\n", "No current tickets for", sd_staff$Owner[i])
          } else {
               print(knitr::kable(x[1:nrow(x), ]))
          }

     cat("\n\\newpage\n")
}
